---
title: "R Notebook"
output: html_notebook
---
Biggest problem encountered so far for rcharts is that there is no rendering of the plots in R notebook.


```{r}
#require(devtools)
#install_github('ramnathv/rCharts')
```


```{r}
library(rCharts)
options(RCHART_WIDTH = 600, RCHART_HEIGHT = 400)
library(knitr)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = F)
```


```{r}
iris
```

```{r}
opts_chunk$set(comment = NA, results = "asis", comment = NA, tidy = F)
names(iris) = gsub("\\.", "", names(iris))
p1 = rPlot(SepalLength ~ SepalWidth | Species, data = iris, color = 'Species', type = 'point')
#p1$print()
p1$print(include_assets=T)
```

```{r}
library(reshape2)
data(tips, package = 'reshape2')
p3 = rPlot(x = 'day', y = 'box(tip)', data = tips, type = 'box')
p3$print(include_assets=T)
```

```{r results = "asis", comment = NA}
r1 <- rPlot(mpg ~ wt, data = mtcars, type = 'point')
```
```


```{r results = "asis", comment = NA}

```


```{r results = "asis", comment = NA}
r1$show('iframe', cdn = TRUE)
```

```{r}
p3$save('boxplot_local_rcharts.html')   # saves it as html, but js, css still point to local machine

##this cdn thing did not work
#link js/css assets from an online cdn
p3$save('boxplot_cdn_rcharts.html', cdn = TRUE) # saves it as html, and js, css point to cdn

#create standalone chart with all assets included directly in the html file
p3$save('boxplot_standalone_rcharts.html', standalone = TRUE) 
```

